Dissecting the causal question underlying the association between cancer and ADRD 

### 2021-03-31 04_reports/manuscript.Rmd
updated manuscript, prints kableextra

---
```{r, echo =  FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.align="center")
source(here::here("02_R", "03_descriptives.R"))
```

@@

>>>>

---
```{r, echo =  FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align="center")
library(survival)
library(tidyverse)
library(tableone)
source(here::here("02_R", "03_descriptives.R"))
```

@@

## Table 1

```{r}
tableone_exp <-
  print(
    tableone,
    explain = TRUE,
    test = FALSE,
    quote = FALSE,
    noSpaces = TRUE,
    printToggle = FALSE
  )

kableExtra::kable(tableone_exp, booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

```
